---
title             : "RMarkdown Manuscript Template"
shorttitle        : "manuscript workflow"

author: 
  - name          : "su"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"

affiliation:
  - id            : "1"
    institution   : "University of Toronto"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
  
  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
  
  One sentence clearly stating the **general problem** being addressed by  this particular study.
  
  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
  
  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
  
  One or two sentences to put the results into a more **general context**.
  
  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
  
  <!-- https://tinyurl.com/ybremelq -->  

keywords          : "rmarkdown"
wordcount         : "x"

bibliography      : "zotero_ref.bib"

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_word
---

```{r chunk_option, include = FALSE}
## Set global chunk options
knitr::opts_chunk$set(echo = FALSE, # make sure this is false 
                      warning = FALSE, 
                      message = FALSE,
                      cache = TRUE,
                      include = FALSE,
                      fig.width = 8,
                      fig.height = 5)
```

```{r library, include=FALSE, message=FALSE}
## Load packages
library("papaja"); library("tidyverse"); library("broom"); library("ggplot2"); library("here")
```

```{r sessioninfo}
# Recording session info for reproducibility
sessionInfo()
```

```{r data}
# import data
source(here("data_analysis", "data_analysis_prep.R"))
```

  Introduction intro...[@aaker_i_2001]  
  blah balh [-@adema_vicarious_2000]  
  yay [@anusic_nature_2009; @apfelbaum_journal_2016]  

# Methods


## Participants
```{r exclusion}
df <- df %>%
  mutate(exclusion = case_when(
    attn_check == "pass" &
      var_low == "acceptable" ~ "eligible",
    TRUE ~ "ineligible"))
```
  We excluded `r length(which(df$exclusion=="ineligible"))` participants who were deemed careless and consistent in their responses.
  
```{r demographics, results='asis'}
demographics <- df %>%
  group_by(gender) %>%
  summarise(n = n(),
            Mean = mean(age, na.rm = T),
            SD = sd(age, na.rm = T),
            Min = min(age, na.rm = T),
            Max = max(age, na.rm = T)) %>% 
  ungroup()

knitr::kable(demographics, digits = 2)
```
As shown in Table 1, `r length(demographics$n[demographics$gender=="female"])` female participants were `r demographics$Mean[demographics$gender=="female"]` years old in average (SD = `r demographics$SD[demographics$gender=="female"]`). 

## Material
### *Regulatory Focus*.  
Promotion and prevention focus was collected using a 15-item measure [@higgins_value_2005]... 

## Procedure
Data was collected throgh Amazon's MTurk...  

## Data analysis
We used `r papaja::cite_r("zotero_ref.bib")` for all our analyses.

# Results
  
```{r lm_model}
lm.model <- glm(profile_num ~ promotion + prevention, 
            family = "poisson",
            data = subset(df, exclusion =="eligible")) %>%
  broom::tidy() 

knitr::kable(lm.model, digits = 3)
```
Consistent with our hypothesis, promotion focus negatively predicted the number of profiles viewed, $\beta$ = `r papaja::printnum(lm.model[2, 2])`, $p$ < `r papaja::printnum(lm.model[2, 5])`...

```{r plot, include=TRUE}

mean_c <- function(x) {
  x - mean(x, na.rm = T)
}
df <- df %>%
  filter(exclusion == "eligible") %>%
  mutate(prom.c = mean_c(promotion),
         prev.c = mean_c(prevention))

condition_label <- c(
  `-1` = "Undesirable-trait strategy",
  `1` = "Desirable-trait strategy")
df %>%
  ggplot() +
  geom_smooth(aes(x = prom.c, y = profile_num),  colour = "blue", method = lm, se = T) +
  geom_smooth(aes(x = prev.c, y = profile_num),  colour = "gold", method = lm, se = T) +
  labs( x = "Regulatory focus", y = "Number of\nProfiles Viewed") +
  facet_wrap(~condition, labeller = as_labeller(condition_label)) + 
  labs(x = "Regulatory Focus", y = "Number of\nProfiles Viewed") +
  papaja::theme_apa()
```
As shown in Figure 1, neither promotion nor prevention focus had an impact on the number of profiles viewed in the undesirable condition, whereas promotion focus but not prevention focus predicted positively the number of profiles viewed in desirable condition.


# Discussion
  My study is important. Please believe me.

\newpage

# References

```{r create_r-references}
papaja::r_refs(file = here("zotero_ref.bib"), append = T)
my_citation <- papaja::cite_r(file = "zotero_ref.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup
